\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
Vertex-Face shouldn't be capitalised in middle of sentence
prefer written to disk to written to file

\subsection{Tessellation of solids (meshing)}
Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap 
detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++. In 
general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to disk 
various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.

@@

\section{Rapid geometry modelling}
Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk 
from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all 
the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved
as a GDML file or visualised using VTK.

>>>>

\subsection{Tessellation of solids (meshing)}
Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap 
detection. For each Geant4 solid instance a triangular tessellated vertex-face mesh is generated and cached. This mesh is then used to determine the extent 
of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++. In 
general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file 
various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.

@@

\section{Rapid geometry modelling}
Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to file 
from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all 
the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved
as a GDML file or visualised using VTK.
